\chapter{Literature survey}
\noindent 
\textbf{ARTICLE 1: Design of Automatic Hand Sanitizer System
Compatible with Various Containers}\\
Summary:
This paper suggests the design of an automatic hand sanitizer system compatible
with various sanitizer containers.

Method:When one moves one’s hand close to the device sensor, the hand sanitizer container is pumped once.

Conclusions: The automatic hand sanitizer device proposed in this paper is ultimately expected to contribute to contactless
hand disinfection in public places and virus infection prevention. Additionally, it is economical and eco-friendly by decreasing
waste emissions..\\ \\
%\vspace{0.4cm}
\textbf{ARTICLE 2: Development of a Non-contact Infrared Thermometer by Jing Zhang
School of Energy Engineering, Yulin University, Yulin,719000, China 
}\\
Summary:
It tells the design of Infrared temperature sensor MLX90614 d to collect human or object temperature by the SCM to process the
temperature into the LCD display and alarm when over-temperature. Using software design to complete the control of the system. The smart thermometer can achieve non-contact measurement,
place the thermometer in the forehead for a few seconds to get the body temperature, to alarm once the set value is exceeded. The design temperature range is 0-55 ℃, and temperature resolution is
0.1 ℃.
 \\ \\
%\vspace{0.4cm}
\textbf{ARTICLE 3:ARTICLE 3:Benchmark Analysis of Jetson TX2, Jetson Nano and Raspberry PI using Deep-CNN by Ahmet Ali Süzen, Burhan Duman, Betül Şen.}\\
In this paper Ahmet Ali Süzen et al. have analysed the performance of Jetson TX2, Jetson Nano and Raspberry PI using Deep-CNN.Hardware, low power consumption, high accuracy and performance are crucial factors for deep learning applications.
High level graphics processing units (GPU) are commonly used in high performance deep learning applications.The analysis was done through CNN algorithm created by using fashion product images dataset. 2D CNN model had been developed by Ahmet Ali Süzen et al. so as to classify 13 different fashion products.The Dataset was comprised of 45K pictures. The analysis showed that, the Jetson TX2 had more power consumption, but it performed better in a shorter time, had higher accuracy than others. Jetson TX2 had the highest in cost 399 dollars because low cost is not possible with high hardware features. Raspberry PI without NVIDIA GPU support was the most cost-effective hardware 35 dollars but it was not the right choice for deep learning applications. Since, the hardware which is going to be used in our project should be cost-effective and efficient in terms of its performance, the best choice was Jetson Nano 99 dollars.
\\ \\
%\vspace{0.4cm}
\textbf{ARTICLE 4: “A Real-Time Face Detection Method Using TensorRT and SSD,” Journal of the Korea Information Processing Society: Software and Data Engineering, vol. 9, no. 10, pp. 323–328, Oct. 2020.
  }\\
Summary:Recently, new approaches that significantly improve performance in object detection and recognition using deep learning technology have been proposed. Of the various techniques for object detection, especially facial object detection (Faster R-CNN, R-CNN, YOLO, SSD, etc), SSD is superior in accuracy and speed to other techniques. In this paper, among object detection networks, Mobilenet v2 network is used, models combined with SSDs are trained, and methods for detecting objects. 
Facial object detector was created by H.-B. Yoo et al. as an application to verify the performance of the proposed method, and its behavior and performance were tested in various situations.From this paper, we got the idea of developing our own mask detector on the similar lines.
 \\ \\
 %\vspace{0.4cm}
\textbf{ARTICLE 5: SSD-Mobilenet Implementation for Classifying Fish Species
Phan Duy Hung and Nguyen Ngoc Kien
}\\
Summary:
The objective of this paper was to provide a method to classify fish species automatically via images.The method presented in this paper was a combination of the advantages of both the SSD and Mobilenet models in order to provide the needed high accuracy.
 \\ \\
 %\vspace{0.4cm}
\textbf{ARTICLE 6: "Jetson-inference-pytorch-collect-detection" Github repository
}\\
Summary:
 From this github repository, we understood how to collect our own datasets for object detection on the jetson nano.In our project, the datasets are masked face and unmasked face pictures.

 \\ \\
 %\vspace{0.4cm}
\textbf{ARTICLE 7: ": "Jetson-inference-pytorch-ssd" Github repository
}\\
Summary:
From this github repository, we learnt how to retrain the ssd-mobilenet object detection model to build the proposed mask detection model on the jetson nano.
\\ \\
 %\vspace{0.4cm}
\textbf{ARTICLE 8: "DEVELOPMENT OF AN AUTOMATIC BODY MASS INDEX MACHINE" by Vincent A. Akpan' Joshua B. Agbogun and Oluwatosin T. Omotehinwa
}\\
Summary:
This paper tells about Obesity, which refers to excess body fat in the body, has become a popular and important public health problem. Body mass index 
(BMI) is metric currently in use for defining obesity or anthropometric height/weight characteristics in adults and for classifying them in groups.It is unarguable that rather than error-prone manual BMI calculations, an automatic BMI computation is a preferred option. This paper presents the design and development of a low-cost automatic BMI machine for indoor and out-door use.The performance of the proposed low-cost automatic BMI machine shows that it can be used in homes, hospitals,companies as well as in any environments where routine BMI monitoring may be desired.Recent study conducted among young adults in Nigeria showed that more than one in every 
eight young adults was either overweight or obese.
\\ \\
 %\vspace{0.4cm}
\textbf{ARTICLE 9: "TOUCH LESS HEART BEAT DETECTION WITH CARDIOPULMONARY ANALYSIS" by S.Ushasukanya
, Alladi Saiteja
, Swaroop Duppala
}\\
Summary:
This paper provides a method for communication with fewer pulse regions and a cardiovascular sign
indicating approaches. Using a vector processor, an electromagnetic device at a gap of 1 m from a
human is made to detect the cardiac pulse signal. The suggested method reveals a constraint on the
detection of pulse signals for the reliability of both repeated and strong modulation. Predictions are
carried out at 2.4, 5.8, 10, 16 and 60 GHz, as well as at various power rates between 0 and-27 dBm. In
consideration of the projections developed for both breathing and heart rates, a model for
cardiopulmonary function is described.The pulse rate and the shift in pulse are separated from the
stimulus being provided by wavelets and incredible channels, for SNR between0 and-20 dB.

\\ \\
 %\vspace{0.4cm}
\textbf{ARTICLE 10: "A novel Face Recognition System based on Jetson Nano developer kit" by Thair A. salih and Mohammad Basman Gh
}\\
Summary:
Real-time face recognition became more important in the last two decade, it
is adopted universally for attacking crime, stopping fraud, ensuring public safety.  It
proves that it is one of the most reliable biometrics security systems because frames
can be taken from cameras without touching or interacting, and those images
recorded and spontaneously validated with existing databases. The methodology
achieved in this work will deal with several challenges like real-time recognition,
cheap, portable, and reliable system. NVIDIA Jetson Nano is used in this work. It is
a tiny, powerful AI computer that delivers the estimated performance to run
advanced AI workloads with a small size, low-power, and low-cost.
\\ \\
 %\vspace{0.4cm}
\textbf{ARTICLE 11: "EVM-CNN: Real-Time Contactless Heart Rate
Estimation from Facial Video" by
Ying Qiu, Yang Liu, Juan Arteaga-Falconi, Haiwei Dong
}\\
Summary:
 it was
shown that heart rate information can be extracted from facial
videos by spatial decomposition and temporal filtering. Inspired
by this, a new framework is introduced in this paper for remotely
estimating the heart rate under realistic conditions by combining
spatial and temporal filtering and a convolutional neural network.
 